---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  fig.path  = "man/figures/README-",
  out.width = "100%",
  warning   = FALSE,
  message   = FALSE
)
```

# Welcome to the dev-version of the library
[flip](http://cran.r-project.org/web/packages/flip/index.html) on CRAN


* * *

## Installation
You can install the flip form CRAN

```{r cran-installation, eval = FALSE}
install.packages("flip")
```

You can install the dev-version of flip from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("livioivil/flip")
```

* * *

## Some examples

```{r load_pkg}
library(flip)
```

### Univariate analysis

Testing the symmetry around 0 in a one sample (i.e. equivalent to one sample t-test) 
```{r one_sample}
set.seed(1)
one_sample <- rnorm(10) + 0.5
test_one_flip  <- flip(one_sample)
summary(test_one_flip)
```

and ploting

```{r one_plot}
plot(test_one_flip) # NOTE: same ad hist(test_flip)
```


### Multivarite analysis
```{r multi_sample}
set.seed(1)
multi_sample    <- data.frame(
  var_one = rnorm(10) + 0.5,
  var_two = rnorm(10)
)
test_multi_flip <- flip(~., data = multi_sample)
summary(test_multi_flip)
plot(test_multi_flip) 
```

Which is different from ploting

```{r multi_hist}
# set `par(mar = c(1, 1, 1, 1))` if you get an error (mostly using Rstudio)
hist(test_multi_flip)
```


* * *

## References

For the general framework of univariate and multivariate permutation tests see: 

*Pesarin, F. (2001) Multivariate Permutation Tests with Applications in Biostatistics. Wiley, New York.*


For analysis of mixed-models see:

*L. Finos and D. Basso (2014) Permutation Tests for Between-Unit Fixed Effectsin Multivariate Generalized Linear Mixed Models. Statistics and Computing. Volume 24, Issue 6, pp 941-952. DOI: 10.1007/s11222-013-9412-6*

*D. Basso, L. Finos (2011) Exact Multivariate Permutation Tests for Fixed Effects in Mixed-Models. Communications in Statistics - Theory and Methods. DOI 10.1080/03610926.2011.627103*


For Rotation tests see: 

*Langsrud, O. (2005) Rotation tests, Statistics and Computing, 15, 1, 53-60*

*A. Solari, L. Finos, J.J. Goeman (2014) Rotation-based multiple testing in the multivariate linear model. Biometrics. Accepted*


The colors of the plots of library flip are mostly taken from `display.wes.palette(5, "Darjeeling")` of [library(wesanderson)](https://github.com/karthik/wesanderson).


## Bug reports
If you encounter a bug, please file a
[reprex](https://github.com/tidyverse/reprex) (minimal reproducible example)
on [github](https://github.com/livioivil/flip/issues).
